**Selective DNA and Protein Isolation from Marine Macrophyte Surfaces**

### 2021-05-10 submission/manuscript.Rmd
Manuscript production.

3\. NIOZ, Department of Marine Microbiology and Biogeochemistry, Royal Netherlands Institute for Sea Research, Utrecht University, The Netherlands

@@

Running title: DNA and protein isolation from macrophyte surfaces

>>>>

3\. Department of Marine Microbiology and Biogeochemistry, Royal Netherlands Institute for Sea Research (NIOZ), Utrecht University, The Netherlands

@@

Running title: Selective isolation from macrophyte surfaces
